Industrial Best Practice

### 2015-03-23 ibp/ibp.tex
Added some summary

\maketitle
\section{Executive Summary, 1p}
This report presents a plan for how to develop and distribute a framework for designing and improving APIs in the context of software evolution and software ecosystems.

\url{http://unilearning.uow.edu.au/report/4bi1.html	}

\section{Problem Formulation, 3p}
This section will describe the problem that we are trying to solve, why it is important and what related products exist on the market today.

@@

\subsection{Related Products}
Exhaustive research has found that there exists very few similar solutions similar to our own. While there are countless books related to the subject, very few actually aim to address the needs of busniness and customers; they are primarily focused on the developer.

@@

\begin{itemize}
\item Increase productivity through uniformity and accessibility of data
\item Develop better customer experiences faster, for mobile and web-based applications
\item Achieve real-time data exchange between platforms and applications
\item Enhance visibility into data consumption to optimize APIs
\end{itemize}

While mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.

\section{Plan and Roadmap, 5p}
As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or frameworks that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{phaal2004technology}, and it is advised that it is updated during the process. The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.

@@

\section{Impact Assessment, 2p}
This section will describe the impact that our framework will have.

@@

>>>>

\maketitle
\section{Executive Summary}
This report presents a plan for how to develop and distribute a framework for designing and improving APIs in the context of software evolution and software ecosystems.

The research behind the framework has been made through reviewing existing literature, and through analysing changes between  different versions on an industry API. The main way of assessing the API has been through measuring the impact it has on its ecosystem. The development of the framework has been supported by a solid technology roadmap, dissemination plan and impact assessment.

The findings of our initial studies show that the changes to APIs have negative effects, and that they primarily affect the users of the API. They also show that modifications to APIs heavily influence the ecosystem.

With this report we conclude that the improvement potential to the current ways of designing APIs is huge. This can especially be achieved by weighing in the needs of the whole ecosystem when designing APIs. We also conclude that there is a large need for a framework such as the one we are proposing, and that it could lead to major improvements in areas such as the open-source community and in web development. The three most important benefits of our paper are:

\begin{itemize}
\item Increased usability of your API
\item Reduced negative impacts when changing your API
\item A software ecosystem existing in symbiosis
\end{itemize}

One limitation to this report is that the development of the framework has not started yet, and that only the initial studies have been started. Another limitation is that the no extensive research on whether or not companies have the desire spend resources that do not have an immediate impact on their revenue.

\section{Problem Formulation}
This section will describe the problem that we are trying to solve, why it is important and what related products exist on the market today.

@@

\subsection{Related Products}
Exhaustive research has found that there exists very few similar solutions similar to our own. While there are countless books related to the subject, very few actually aim to address the needs of business and customers; they are primarily focused on the developer.

@@

\begin{itemize}
\item Increase productivity through uniformity and accessibility of data
\item Develop better customer experiences faster, for mobile and web-based applications
\item Achieve real-time data exchange between platforms and applications
\item Enhance visibility into data consumption to optimise APIs
\end{itemize}

While Mashery have a more business oriented approach, they do not offer anything resembling a framework for both business and developers to use when making API design decisions.

\section{Plan and Roadmap}
As mentioned in Section 2, the effects modifications to APIs have on the platform’s ecosystem are explored as being negative. However, there are no existing systematic guidelines or frameworks that take the ecosystem into account for how to best modify an API. Our proposed process for creating such a framework can be seen in Figure \ref{fig:roadmap}. This is an initial version of the roadmap \cite{phaal2004technology}, and it is advised that it is updated during the process. The main reason for this is that it is important to adapt to changes in the market, and if new needs are identified, the strategy should be redesigned to meet them.

@@

\section{Impact Assessment}
This section will describe the impact that our framework will have.

@@

The knowledge gained from the course has had both immediate and long term effects. Immediately, we were able to use the information regarding finding research topics, collaborating with industry and performing research. These topics were invaluable for us when it came to finding a research topic and company for our thesis. In regards to the long term value, information for working at a company or in a professional environment will undoubtedly be of use for us.

The guest lectures were very useful as we received first hand accounts of how research is conducted within industry. This was particularly valuable given how our our solution is heavily involved with research and academia. If either of us wish to pursue a career in research, we now have some idea of what it would require and to some extent what it might be like to do so.

The second guest lecture was also of great help when for this report. The methods and ideas presented were vital in helping us generate ideas and solutions to our given problem.
